Collate Rarefied Samples and Null Models

### 2022-04-21 analysis/04_collate_rarefied_null.Rmd

#read in CWM metrics
path <- here::here("data", "rarefied_metrics", "cwm")
filelist <-  dir(path, "*.rda") %>%
  paste0(path, "/", .)

cwm_metrics <- purrr::map_dfr(filelist, function(x) {
  load(x)
  rarefyID <- str_match(x,"_cell\\s*(.*?)\\s*_sample")[,2]

@@

    cwm_metrics <- cwm_metrics$CWM %>%
      rownames_to_column("YEAR") %>%
      mutate(YEAR = as.integer(YEAR)) %>%
      left_join(cwm_metrics %>% select(-CWM)) %>%
      mutate(rarefyID = rarefyID)

>>>>

#read in CWM metrics
path <- here::here("data", "rarefied_metrics", "cwm_noscale")
filelist <-  dir(path, "*.rda") %>%
  paste0(path, "/", .)

cwm_metrics <- purrr::map_dfr(filelist, function(x) {
  #browser()
  load(x)
  rarefyID <- str_match(x,"_cell\\s*(.*?)\\s*_sample")[,2]

@@

    cwm_metrics <- cwm_metrics %>%
      unnest(CWM) %>%
      mutate(YEAR = as.integer(YEAR), rarefyID = rarefyID)
